A holomorphic approach to membranes and fivebranes

### 2022-06-14 fivebranes/twisted.tex
updates to twisted

The $L_\infty$ structure on the sheaf of holomorphic sections of $L_X$ is described as follows. 
First, $\d = [-]_1$, the differential, is simply given by 
\begin{align*}
\d \beta & = \del \beta \in \Omega^1_X \subset L_{X,-} \\
\d \mu & = \div \mu \in \cO_X \subset L_{X, -}
\end{align*}
and $\d \gamma = \d \nu = 0$. 
For $k \geq 2$ the general formula for the $k$-ary brackets is 
\begin{align*}
[\nu_1, \ldots, \nu_{k-2}, \mu_1,\mu_2]_{k} & = \div(\nu_1 \cdots \nu_k \mu_1 \wedge \mu_2) \\
[\nu_1,\ldots, \nu_{k-3}, \mu_1,\mu_2,\gamma]_k & = \nu_1 \cdots \nu_{k-3} (\mu \wedge \mu') \vee \del \gamma \\
[\nu_1,\ldots,\nu_{k-2}, \mu, \gamma]_k & = \nu_1 \cdots \nu_{k-2} \mu \vee \del \gamma \\
[\gamma_1,\gamma_2]_2 & = \Omega^{-1} \left(\del \gamma_1 \wedge \del \gamma_2 \right) .
\end{align*}
In \cite{RSW} it is shown that this endows $L_{X}$ with the structure of a sheaf of $\Z/2$ graded $L_\infty$ algebras.
There is a sub sheaf given by the sections $\mu$ and $\nu$ which is $L_\infty$-equivalent to the sheaf of holomorphic divergence-free vector fields on $X$.

@@

In \cite{RSW} we gave descriptions of twisted versions of these backgrounds. We recall the results therein, adapted to our situation.

@@

The theory in the backreacted geometry will be defineed to be a deformation of the 11d theory placed on the complement of the zero section. The complement of the zero section admits additional structures inherited from the obvious THF structure on $\R \times X$. Note that $\R\oplus V$ has an obvious rank 1 subbundle together with a complex structure on the quotient. Accordingly, we may choose as fiber coordinates $t, w_{1}, w_{2}, \bar w_{1}, \bar w_{2}$ and a fiberwise partially hermitian metric $h$. Explicitly, the corresponding norm is given by
\begin{align*}
 \pi:  \R\times X & \to \R_{+} \\
  (t, w_{i}, \bar{w_{i}}, p)& \mapsto t^{2} + |w_{1}|^{2}+|w_{2}|^{2}
\end{align*}
Letting $p : \R\times X \to Z$, we have an $S^{4}$-bundle $(\pi, p) : \R\times X - Z \to \R_{>0}\times Z$. The fiber spheres have a canonical foliation

>>>>

The $L_\infty$ structure on the sheaf of holomorphic sections of $L_X$ is described as follows. 
First, $\d = [-]_1$, the differential, is simply given by 
\begin{align*}
\d \beta & = \del \beta \in \Omega^1_X \subset L_{X,-} \\
\d \mu & = \div \mu \in \cO_X \subset L_{X, -}
\end{align*}
and $\d \gamma = \d \nu = 0$. 
For $k \geq 2$ the general formula for the $k$-ary brackets is 
\begin{align*}
[\nu_1, \ldots, \nu_{k-2}, \mu_1,\mu_2]_{k} & = \div(\nu_1 \cdots \nu_k \mu_1 \wedge \mu_2) \\
[\nu_1,\ldots, \nu_{k-3}, \mu_1,\mu_2,\gamma]_k & = \nu_1 \cdots \nu_{k-3} (\mu \wedge \mu') \vee \del \gamma .\\
[\nu_1,\ldots,\nu_{k-2}, \mu, \gamma]_k & = \nu_1 \cdots \nu_{k-2} \mu \vee \del \gamma .
\end{align*}
In \cite{RSW} it is shown that this endows $L_{X}$ with the structure of a sheaf of $\Z/2$ graded $L_\infty$ algebras.
There is a sub sheaf given by the sections $\mu$ and $\nu$ which is $L_\infty$-equivalent to the sheaf of holomorphic divergence-free vector fields on $X$.

@@

In \cite{RSW} we gave descriptions of twisted versions of these backgrounds. We recall this construction, adapted to a slightly more global situation. We will consider the eleven-dimensional theory on 11-manifolds that arise as total spaces of vector bundles. Placing the theory in the backreacted geometry is a 3-step procedure:

\begin{itemize}
  \item Place the eleven dimensional theory on the complement of the zero section. To do so, we will wish to describe the complement of the zero-section in a way that facilitates natural operations on holomorphic-topological local $L_{\infty}$-algebras.

  \item Deform the theory on the complement of the zero section by a certain maurer-cartan element. The Maurer-Cartan element is thought of as the flux sourced by branes wrapping the zero section.

  \item The complement of the zero section is a manifold with boundary - we impose a natural boundary condition.

\end{itemize}

@@

We begin by describing the complement of the zero section
\[
\R\oplus V \setminus 0\times Z
\]. Note that $\R \times X$ is equipped with a natural transverseley-holomorphic foliation. That is, there is a rank 1 subbundle $\R\subset \R\oplus V$ together with a complex structure on the quotient. Accordingly, we may choose as fiber coordinates $t, w_{1}, w_{2}, \bar w_{1}, \bar w_{2}$ and a fiberwise partially hermitian metric $h$. Explicitly, the corresponding norm is given by
\begin{align*}
 \pi:  \R\times X & \to \R_{+} \\
  (t, w_{i}, \bar{w_{i}}, p)& \mapsto t^{2} + |w_{1}|^{2}+|w_{2}|^{2}
\end{align*}
Letting $p : \R\times X \to Z$, we have an $S^{4}$-bundle $(\pi, p) : \R\times X - Z \to \R_{>0}\times Z$. The vertical tangent bundle of this $S^{4}$ bundle inherits a natural subbundle coming from the THF structure of the ambient manifold; the fibers of this subbundle equip
